### 2025-08-27 evaluating-prediction-accuracy.qmd
20250827 - tweaks

- [discrimination](#sec-discrimination):
  - [adjusted $R^2$](#sec-adjustedRsquared)
- [calibration](#sec-calibration):
  - [calibration plot](#sec-calibrationPlot)
- [general accuracy](#sec-calibration):
  - [MAE](#sec-meanAbsoluteError)
  - [RMSE](#sec-rootMeanSquaredError)

>>>>

- [discrimination](#sec-discrimination):
  - [standardized regression coefficient (beta)](#sec-standardizedRegressionCoefficient)
- [calibration](#sec-calibration):
  - [calibration plot](#sec-calibrationPlot)
- [general accuracy](#sec-calibration):
  - [calibration plot](#sec-calibrationPlot)
  - [adjusted $R^2$](#sec-adjustedRsquared)
  - [MAE](#sec-meanAbsoluteError)
  - [RMSE](#sec-rootMeanSquaredError)
